\tool: Revisiting BadUSB with Type-C

### 2021-03-22 WOOT/Files/experiment.tex
fuck caps
fuck

		\begin{tabular}[c]{@{}c@{}}Lenovo Xiaoxin Pro 13\\ 2020\end{tabular} & Windows 10 (OS Build 18363.1379)                                                                         & Pop-up                    & ``Win+P''-\textgreater{}Mouse click on `Duplicate' Option \\ \hline

@@

In the experiment of HID emulator mode, we used {Lenovo Xiaoxin Pro 13
2020}, a PC with Windows 10 \mbox{(OS Build 18363.1379)} and Ubuntu 20.04.2 LTS with two \ac{USB} Type-C interfaces as the
target devices. During this experiment, \tool disguised itself as a normal keyboard and an external screen as feedback channel. When first plugged in, the victim's device raised a pop-up window asking the victim which mode should the new screen be set to. \tool immediately injected a sequence of mouse movements and clicks to set itself as a mirror to the primary monitor. Thus we had successfully completed the attack initialization. Then we tested three scripts, ranging from reverse shell backdoor to malware payload execution, all of them resulted in success. Compared to original BadUSB attacks like Rubber Ducky, our \tool can provide attackers real-time feedback which allows attackers to perform more accurate attacks.
%This also warned us that we need more thorough defense against such BadUSB
%attack.

@@

During the experiment of privacy extraction via our video capture mode, we chose \mbox{\textit{HUAWEI P30 (ELE-AL00)}}, a
smartphone in \mbox{EMUI 11.0.0.135(C00E128R2P5)} \mbox{(Android 10.0 based)} with a \ac{USB} Type-C interface, as the
target device. In the privacy extraction experiment, \tool passively captured video
from the victim's device and used \textit{OpenCV} to identify the sensitive
information from the video stream.  When the victim viewed text or photos with
text, \tool used the techniques of \ac{OCR}  to
extract text from corresponding video frames. In this experiment, the attacker
successfully extracted text such as name, address, ID number, and other sensitive
personal information. We also tested the payment code extractor, which enables
an attacker to identify payment code in the video stream and performs transactions
without the password. During our experiment, we noticed that this HUAWEI device supports `Desktop Mode'
for its external screen, which enables user to use their devices like a desktop computer with an external screen.
If \tool is set into this mode, \tool is able to inject mouse movements to set itself into mirroring the primary screen, as we discussed in Section~\ref{subsec:attack_init}.
As this is also a part of our case study, more details about
the extracted sensitive data can be found in Section~\ref{subsec:case_study} and
Table~\ref{table:information_extracted}.

>>>>

		\begin{tabular}[c]{@{}c@{}}Lenovo Xiaoxin Pro 13\\ 2020\end{tabular} & Windows 10 (OS Build 18363.1379)                                                                         & Pop-up                    & ``Win+P''-\textgreater{}Mouse click on ``Duplicate'' Option \\ \hline

@@

In the experiment of HID emulator mode, we used {Lenovo Xiaoxin Pro 13
2020}, a PC with Windows 10 \mbox{(OS Build 18363.1379)} and Ubuntu 20.04.2 LTS with two \ac{USB} Type-C interfaces as the
target devices. During this experiment, \tool disguised itself as a normal keyboard and an external screen as a feedback channel. When first plugged in, the victim's device raised a pop-up window asking the victim which mode should the new screen be set to. \tool immediately injected a sequence of mouse movements and clicks to set itself as a mirror to the primary monitor. Thus we had successfully completed the attack initialization. Then we tested three scripts, ranging from reverse shell backdoor to malware payload execution, all of them resulted in success.
Compared with original BadUSB attacks like Rubber Ducky, our \tool can provide attackers real-time feedback, which allows attackers to conduct more accurate attacks.
%This also warned us that we need more thorough defense against such BadUSB
%attack.

@@

During the experiment of privacy extraction via our video capture mode, we chose \mbox{\textit{HUAWEI P30 (ELE-AL00)}}, a
smartphone in \mbox{EMUI 11.0.0.135(C00E128R2P5)} \mbox{(Android 10.0 based)} with a \ac{USB} Type-C interface, as the
target device. In the privacy extraction experiment, \tool passively captured video
from the victim's device and used \textit{OpenCV} to identify the sensitive
information from the video stream.  When the victim viewed text or photos with
text, \tool used the techniques of \ac{OCR}  to
extract text from corresponding video frames. In this experiment, the attacker
successfully extracted text such as name, address, ID number, and other sensitive
personal information. We also tested the payment code extractor, which enables
an attacker to identify payment code in the video stream and performs transactions
without the password. During our experiment, we noticed that this HUAWEI device supports ``Desktop Mode''
for its external screen, which enable users to use their devices as if they were using a computer with an external monitor.
If \tool is set into this mode, \tool is able to inject mouse movements to set itself into mirroring the primary screen, as we discussed in Section~\ref{subsec:attack_init}.
As this is also a part of our case study, more details about
the extracted sensitive data can be found in Section~\ref{subsec:case_study} and
Table~\ref{table:information_extracted}.
